Home

### 2025-07-20 index.qmd
Enhance index.qmd and styles.css for improved layout and responsiveness
Updated index.qmd to consolidate Professor Bin Yu's titles for clarity. Added responsive styles in styles.css to ensure a mobile-friendly layout, including adjustments for column stacking and image proportions.
Update index.qmd

Chancellor's Distinguished Professor of Statistics  
Statistics Department Chair, 2009 - 2012  
Professor of Electrical Engineering and Computer Sciences, by courtesy

>>>>

CDSS Chancellor's Distinguished Professor of Statistics, Electrical Engineering and Computer Sciences, and Center for Computational Biology
Statistics Department Chair, 2009 - 2012
